Inspiring Confidence and Easing Insecurity in the Pre-election period: The Effect of Recruiting Military Veterans on Confidence in 2024 US Elections

### 2025-07-04 index.qmd
manuscript update with revisions after review

# custom function to return a certain selection of logistic regression model
# goodness-of-fit statistics
lrm.gof.stats <- function(x, ...){

  out <- data.frame(
    null.deviance = x$null.deviance,
    df.null = x$df.null,
    logLik = as.numeric(stats::logLik(x)),
    AIC = stats::AIC(x),
    BIC = stats::BIC(x),
    deviance = stats::deviance(x),
    df.residual = stats::df.residual(x),
    nobs = stats::nobs(x),
    chisq = as.numeric(x$null.deviance - stats::deviance(x)),
    df = as.numeric(x$df.null - stats::df.residual(x)),
    'P(>chi)' = pchisq(q=x$null.deviance - stats::deviance(x),
                       df = x$df.null - stats::df.residual(x), 
                       lower.tail = F)
  )
  out <- dplyr::as_tibble(out)
  return(out)
}

@@

The question emerged in light of the recent surge of efforts nationwide to recruit veterans to serve as election workers [@lawrence2022; @wentling2024] midst an environment where election insecurities were heightened and intensified. Bearing that in mind, the heightened insecurities in anticipation of upcoming elections do not merely pertain to the election outcome (e.g., who wins), but to one's general sense of confidence in the integrity of elections administration and to the safety of casting a ballot in-person.

@@

Those in the treatment condition had lower probability to express that they were 'Very' or 'Somewhat' concerned for violence in Maricopa County, AZ Elections, yet higher probability of expressing 'Not too' or 'Not at all' concerned. As for confidence in voter safety, moving from treatment to control, the difference in predicted probability of a respondent selecting "Very Confident" was $0.08$. @tbl-preds-diff1 and @tbl-preds-diff2 show the significant differences in predicted probabilities at 95$\%$ confidence^[The same models were run for items pertaining to safety concerns in one's local area but results of the treatment were not significantly different from the control. See Appendix D for full results table of ordinal logistic regression]. These findings support both H~4a~ and H~4b~ respectively, permitting rejection of the null for each hypothesis.

@@

@@

As stated previously, the survey was fielded on a non-probability sample of 1,287 U.S. citizens 18 years of age or older. The results presented here are not assumed to be generalizable to the national population. It may be feasible to weigh the sample to demographics of the population at the time the survey was fielded, but this is unnecessary for the experimental purpose of the study. If similar findings complement or replicate these results, then the expense of drawing samples more representative of the national population may be justified. At this stage, however, the results are limited to demonstrating treatment effects that are sample dependent.

It is difficult to compare magnitude of effect with other studies given that the item number, item wording, measurement, and computation of confidence in elections is unique across most individual studies to include this one. For instance, @gaudette2025 doesn't compose multiple items into a single composite measure, but subtracts pre-treatment values from post-treatment values for single-item measures with Likert-style response options. Whereas @clayton2023 develops a scale referred to as "Trust in American electoral process" by taking the mean from three items. The item wording of that scale is markedly similar to the items used to compose the trust scale of this study, but the range of response options differs considerably. Thus, while most studies examining public confidence in elections often include the core question "How confidence are you that your vote \[will be/was\] counted as you intended in the most recent election?", the different ways that researchers measure and compute variable scores on the outcome are most often, and unfortunately, sample dependent. The study of public confidence in elections is in desperate need of a standard method of measurement, or even a screened and validated item bank, and this study may be seen as a baby step to that end.

@@

The data of the current study is limited in helping to discern whether the treatment garners greater confidence in elections uniformly across different racial or ethnic groups given that the largest proportion of the sample identified their race as White (77%). It is reasonable to suspect that the treatment vignette might differ by race and ethnicity, but the sample is insufficient to make such generalizations. Nevertheless, attitudes about veterans that differ by group may play an important role in determining whether publicized efforts to recruit military veterans boosts confidence in elections uniformly or whether the effect is merely partial to certain segments of the population. In their research examining whether groups differed in attitudes about veterans, @kleykamp2018 could only speculate as to why levels of support were lowest among Hispanic and Black respondents. Other research has found that attitudes about the U.S. military generally---though not about active or veteran military service members in particular---differs by race and ethnicity to varying extents, but could not supply reason for one groups' sentiment over another [@nichols2015].

Other studies have drawn out disparities in public attitudes about veterans but in ways that are mostly indirect, i.e., without assessing public regard for veterans directly. One overarching issue is that there's limited research that differentiates public regard for veteran and active military service members from the U.S. military as an institution in general. For instance, some studies assess public regard for veterans indirectly by examining whether, and to what extent, endorsement of certain policies differentiate by whether such policies benefit veterans or the public generally. In one such study, Republican partisanship was shown to be the most consistent factor associated with more favorable attitudes on homelessness and PTSD among the veteran population, but not among the general adult population [@tsai2021].

The bluntness of the experimental stimulus and survey items don't allow us to establish exactly what it is about military veterans in particular that cues stronger confidence in elections. No survey items assessed public attitudes about military veterans specifically, pre- nor post-treatment. This unfortunately leaves no room for me to postulate and examine any potential mechanisms underlying results. As such, a question lingers about whether some antecedent mechanism transmits (i.e., mediates) the effects of the veteran treatment vignette to the outcome. To put simply, this study reiterates that there *is* something special about veterans in particular that elicits greater confidence in elections, but cannot go further in determining exactly *what* that special something might be.

Factors that *moderate* the relationship of the treatment on the outcome of interest are likely plenty, but one can only offer conjecture of a *mediator* driving results. One potential explanation is that veterans, and all those who serve in the military, potentially function as a national symbol. The group is abstract just as the nation is abstract, and the potency of the veteran group emulates the potency of a national symbol. Recall Benedict Anderson's [-@anderson2006] meditation on the Tomb of the Unknown Soldier, "...saturated with ghostly *national* imaginings" [-@anderson2006, 9, emphasis original]. In various studies, national symbols such as the flag, the national anthem, or even mere appeal to national identity have potent, yet variable, effects on different outcomes [@schatz2007; @butz2007; @kemmelmeier2008; @butz2009; @gangl2016; @kalmoe2016; @levendusky2018]. It is plausible that military service members and veterans function in much the same way---as a symbol of national loyalty, pride, and nationalism for people to praise and revere out of a sense of duty prescribed by social norm and reinforced by national sentiment. As such, it may be the case that the treatment effect on confidence in elections is mediated through an affective response to a national symbol---in this case, veterans. The veteran cue may indeed stimulate national sentiment and subsequently boost confidence in elections.

@@

@@

```{r}
#| label: tbl-demog
#| tbl-cap: "Sample Demographics"
#| tbl-colwidths: [70]
#| tbl-pos: H

# descriptive stats of categorical variables
# gtsummary method
gtsummary::theme_gtsummary_compact()

tbl.desc <- data |>  
  gtsummary::tbl_summary( 
    by = group,
    label = list(
      age_cat = "Age group, in years",
      gender = "Gender",
      race = "Race",
      hisp = "Hispanic, Latino, or Spanish origin?",
      educ_4cat = "Education"
      ),
    include = c(
      age_cat,
      gender,
      race,
      hisp,
      educ_4cat
      ),
    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
    missing = "ifany",
    missing_text = "NA") |> 
  gtsummary::add_overall() |> 
  gtsummary::modify_header(label = "**Variable**") |> 
  gtsummary::bold_labels()

tbl.desc |>
  gtsummary::as_tibble() |>
  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
                "**Control (N = 637)**" = "**Control**  \nN = 637",
                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
  tinytable::tt(theme = "spacing") |>
  tinytable::format_tt(markdown = T) |>
  tinytable::format_tt(replace = " ") |>
  tinytable::style_tt(fontsize = 0.70, align = "lccc")

@@

```{r}
#| label: tbl-demog2
#| tbl-cap: "Sample Demographics"
#| tbl-colwidths: [70]
#| tbl-pos: H

tbl.desc2 <- data |>  
  gtsummary::tbl_summary( 
    by = group,
    label = list(
      partyid_3cat = "Party ID",
      ideo_3cat = "Political Ideology",
      ideolean = "If R had to choose Political Ideology",
      voted2020 = 'Did R Vote in 2020 Election',
      choice2020 = 'Vote Choice in 2020 Election',
      voteintent = 'Intent to Vote in 2024 Election'),
    include = c(
      partyid_3cat,
      ideo_3cat, 
      ideolean, 
      voted2020, 
      choice2020),
    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
    missing = "ifany",
    missing_text = "NA") |> 
  gtsummary::add_overall() |> 
  gtsummary::modify_header(label = "**Variable**") |> 
  gtsummary::bold_labels()

tbl.desc2 |>
  gtsummary::as_tibble() |>
  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
                "**Control (N = 637)**" = "**Control**  \nN = 637",
                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
  tinytable::tt(theme = "spacing") |>
  tinytable::format_tt(markdown = T) |>
  tinytable::format_tt(replace = " ") |>
  tinytable::style_tt(fontsize = 0.70, align = "lccc")

```{r}
#| label: tbl-demog3
#| tbl-cap: "Sample Demographics"
#| tbl-colwidths: [70]
#| tbl-pos: H

tbl.desc3 <- data |>  
  gtsummary::tbl_summary( 
    by = group,
    label = list(
      milserv1 = "Military Service",
      milserv2 = "Current Active Duty",
      milservfam = "Military Service within Family?"
      ),
    include = c(
      milserv1,
      milserv2, 
      milservfam), 
    type = list(
      milserv1 ~ "categorical",
      milserv2 ~ "categorical",
      milservfam ~ "categorical"
      ),
    statistic = list(gtsummary::all_categorical()~ "{n} ({p}%)"), 
    missing = "ifany",
    missing_text = "NA") |> 
  gtsummary::add_overall() |> 
  gtsummary::modify_header(label = "**Variable**") |> 
  gtsummary::bold_labels()

tbl.desc3 |>
  gtsummary::as_tibble() |>
  dplyr::rename('**Overall (N = 1287)**' = "**Overall**  \nN = 1,287",
                "**Control (N = 637)**" = "**Control**  \nN = 637",
                "**Treatment (N = 650)**" = "**Treatment**  \nN = 650") |>
  tinytable::tt(theme = "spacing") |>
  tinytable::format_tt(markdown = T) |>
  tinytable::format_tt(replace = " ") |>
  tinytable::style_tt(fontsize = 0.70, align = "lccc")

## Test of Random Assignment to Experiment Condition

@@

tab.logit <- modelsummary::modelsummary(m1, 
                           output = "tinytable", 
                           estimate = "{estimate},  [{conf.low}, {conf.high}]",
                           statistic = NULL,
                           coef_map = cmp, 
                           gof_map = NA)

# create 2nd table containing only logit model fit statistics
# using custom function, get logit regression model fit stats... 
gof_stats <- lrm.gof.stats(m1) |> 
  # omit certain stats (saves space)
  dplyr::select(
    nobs, logLik, df, chisq, P..chi., deviance, null.deviance,
    -AIC, -BIC, -df.null, -df.residual) |> 
  # rename column variables
  dplyr::rename(
    "Num.Obs"       = "nobs",
    "Null Deviance" = "null.deviance",
    "Deviance"      = "deviance",
    "DF"            = "df",
    "Log.Lik"       = "logLik",
    "chisq"       = "chisq",
    "P(>chisq)"   = "P..chi."
  ) |> 
  # pivot into two column long-form dataframe
  tidyr::pivot_longer(cols = everything(),names_to = " ", values_to = '**log(OR)**') |>
  # pipe into tinytable
  tinytable::tt(width = 0.8) |> 
  # ensure rows with math text are identified and formatted as math (i.e., $..$)
  tinytable::format_tt(i = c(4,5), j = 1, math = T)

# using `rbind2` function, bind 2nd table at bottom of first table 
tinytable::rbind2(tab.logit, gof_stats, use_names = F, headers = F) |> 
  # add horizontal line just above fit stats
  tinytable::style_tt(i = 16, line = "t", line_color = "black", line_width = 0.1) |>
  # adjust fontsize of text within table
  tinytable::style_tt(fontsize = 0.7, align = "lc") |>
  # finally, format markdown and blank out any NA fillers
  tinytable::format_tt(markdown = T, replace = " ")

@@

# Appendix C: Polychoric Item and Score Correlations of Trust and Distrust {.appendix}

@@

# Appendix D: Predicted Probabilities of Safety Concerns by Treatment Condition {.appendix}

@@

[^9]: See Appendix C for Inter-item correlation analysis.

>>>>

# custom function to return a certain selection of logistic regression model
# goodness-of-fit statistics
lrm.gof.stats <- function(model, ...){

  out <- data.frame(
    nobs = stats::nobs(model),
    null.deviance = model$null.deviance,
    df.null = model$df.null,
    logLik = as.numeric(stats::logLik(model)),
    deviance = stats::deviance(model),
    df.residual = stats::df.residual(model),
    chisq = as.numeric(model$null.deviance - stats::deviance(model)),
    df = as.numeric(model$df.null - stats::df.residual(model)),
    'P(>chi)' = pchisq(q=model$null.deviance - stats::deviance(model),
                       df = model$df.null - stats::df.residual(model), 
                       lower.tail = F)
  )
  out <- dplyr::as_tibble(out) |>  
  # rename column variables
  dplyr::rename(
    "Num.Obs."      = "nobs",
    "Log.Lik"       = "logLik",
    "Deviance"      = "deviance",
    "Deviance Null" = "null.deviance",
    "DF"            = "df",
    "chisq"          = "chisq",
    "P(>chisq)"     = "P..chi."
  )
  return(out)
}

@@

@@

Those in the treatment condition had lower probability to express that they were 'Very' or 'Somewhat' concerned for violence in Maricopa County, AZ Elections, yet higher probability of expressing 'Not too' or 'Not at all' concerned. As for confidence in voter safety, moving from treatment to control, the difference in predicted probability of a respondent selecting "Very Confident" was $0.08$. @tbl-preds-diff1 and @tbl-preds-diff2 show the significant differences in predicted probabilities at 95$\%$ confidence^[The same models were run for items pertaining to safety concerns in one's local area but results of the treatment were not significantly different from the control. See Appendix E for full results table of ordinal logistic regression]. These findings support both H~4a~ and H~4b~ respectively, permitting rejection of the null for each hypothesis.

@@

## Limitations

The bluntness of the experimental stimulus and survey items don't allow us to establish exactly what it is about military veterans in particular that cues stronger confidence in elections. No survey items assessed public attitudes about military veterans specifically, pre- nor post-treatment. This unfortunately leaves no room for me to postulate and examine any potential mechanisms underlying results.

@@

@@

As stated previously, the survey was fielded on a non-probability sample of 1,287 U.S. citizens 18 years of age or older. The results presented here are not assumed to be generalizable to the national population. It may be feasible to weigh the sample to demographics of the population at the time the survey was fielded, but this is unnecessary for the experimental purpose of the study. If similar findings complement or replicate these results, then the expense of drawing samples more representative of the national population may be justified. At this stage, however, the results are limited to demonstrating treatment effects.

The research question emerged in light of the recent surge of efforts nationwide to recruit veterans to serve as election workers [@lawrence2022; @wentling2024] midst an environment where election insecurities were heightened and intensified. Heightened insecurities in anticipation of upcoming elections do not merely pertain to the election outcome (e.g., who wins), but to one's general sense of confidence in the administration of elections, the integrity of the electoral process, and to the safety of casting a ballot in-person. This study demonstrated that information neutral to the trustworthiness of election administration can not only improve trust in elections, but simultaneously reduce distrust in elections. Those who were presented information about veteran recruitment efforts reported greater trust that votes will be counted accurately, that election staff will competently administer elections, that election technology will be secure from nefarious tampering, and that the process will be fair for all involved. Moreover, those presented with information about veteran recruitment efforts reported lower expectations that electoral fraud will occur. They also felt that election sites would be safe for voters to cast a ballot in person and were less concerned about potential violence compared to those who were not presented information about veteran recruitment efforts.

Confidence in elections was greater among those who read the treatment vignette announcing efforts to recruit veterans to work as election staff and volunteers, but this effect was conditional on whether survey questions asked about elections Maricopa County, AZ. When survey questions asked about elections in one's local area, confidence in elections among the treatment group was not significantly different from the control group. However, the sample's confidence in their local area elections was high in general relative to elections in Maricopa County, AZ (@fig-dist). The results presented here suggest that the effect of the veteran cue in the treatment vignette is compensatory. That is, the gap in confidence in local elections and elections in Maricopa County is reduced by the veterans cue, therefore compensating for the otherwise lower confidence and greater insecurity in Maricopa County elections.

A question lingers about whether some antecedent mechanism transmits (i.e., mediates) the effects of the veteran treatment vignette to the outcome. To put simply, this study reiterates that there *is* something special about veterans in particular that elicits greater confidence in elections, but cannot go further in determining exactly *what* that special something might be. Factors that *moderate* the relationship of the treatment on the outcome of interest are likely plenty, but one can only offer conjecture of a *mediator* driving results.

One potential explanation is that veterans, and all those who serve in the military, potentially function as a national symbol. The group is abstract just as the nation is abstract, and the potency of the veteran group emulates the potency of a national symbol. Recall Benedict Anderson's [-@anderson2006] meditation on the Tomb of the Unknown Soldier, "...saturated with ghostly *national* imaginings" [-@anderson2006, 9, emphasis original]. In various studies, national symbols such as the flag, the national anthem, or even mere appeal to national identity have potent, yet variable, effects on different outcomes [@schatz2007; @butz2007; @kemmelmeier2008; @butz2009; @gangl2016; @kalmoe2016; @levendusky2018]. It is plausible that military service members and veterans function in much the same way---as a symbol of national loyalty, pride, and nationalism for people to praise and revere out of a sense of duty prescribed by social norm and reinforced by national sentiment. As such, it may be the case that the treatment effect on confidence in elections is mediated through an affective response to a national symbol---in this case, veterans. The veteran cue may indeed stimulate national sentiment and subsequently boost confidence in elections.

@@

It is difficult to compare magnitude of effect with other studies given that the item number, item wording, measurement, and computation of confidence in elections is unique across most individual studies to include this one. For instance, @gaudette2025 doesn't compose multiple items into a single composite measure, but subtracts pre-treatment values from post-treatment values for single-item measures with Likert-style response options. Whereas @clayton2023 develops a scale referred to as "Trust in American electoral process" by taking the mean from three items. The item wording of that scale is markedly similar to the items used to compose the trust scale of this study, but the range of response options differs considerably. Thus, while most studies examining public confidence in elections often include the core question "How confidence are you that your vote \[will be/was\] counted as you intended in the most recent election?", the different ways that researchers measure and compute variable scores on the outcome most often produces results that are, unfortunately, sample dependent. The study of public confidence in elections is in desperate need of a standard method of measurement, or even a screened and validated item bank, and this study may be seen as a baby step to that end.

The data of the current study is limited in helping to discern whether the treatment garners greater confidence in elections uniformly across different racial or ethnic groups given that the largest proportion of the sample identified their race as White (77%). It is reasonable to suspect that the treatment vignette might differ by race and ethnicity, but the sample is insufficient to make such generalizations. Nevertheless, attitudes about veterans that differ by group may play an important role in determining whether publicized efforts to recruit military veterans boosts confidence in elections uniformly or whether the effect is merely partial to certain segments of the population.

In their research examining whether groups differed in attitudes about veterans, @kleykamp2018 could only speculate as to why levels of support were lowest among Hispanic and Black respondents. Their study was distinctive in that it stands as a rare case in which public attitudes about veteran military members was the specific focus of inquiry as opposed to studies that examine public opinion about the military in general. Other research has found that attitudes about the U.S. military generally---though not about active or veteran military service members in particular---differs by race and ethnicity to varying extents, but also could not supply reason for one groups' sentiment over another^[Note, however, that the sample examined by @nichols2015 was constrained to Texas residents, and the military-related issues concerned, among other things, favor for reinstatement of a military draft, support for allowing undocumented immigrants who live in the U.S. to serve in the U.S. Armed Forces, and whether undocumented immigrants should be granted U.S. citizenship as a result of military service. Although the authors found high overall support for the military as an institution, the other military-related attitudes of interest diverge far from public opinion about veterans. As such, differential effects found among different racial or ethnic groups likely have little to do with attitudes about former or active military service members.] [@nichols2015].

Other studies have drawn out disparities in public attitudes about veterans but in ways that are mostly indirect, i.e., without assessing public regard for veterans directly. One overarching issue is that there's limited research that differentiates public regard for veteran and active military service members from the U.S. military as an institution in general. Some studies assess public regard for veterans indirectly by examining whether, and to what extent, endorsement of certain policies differentiate by whether such policies benefit veterans or the public generally. In one such study by @tsai2021, Republican partisanship was shown to be the most consistent factor associated with more favorable attitudes (e.g., compassion) toward homelessness and PTSD among the veteran population, but not among the general adult population. Additionally, Republican partisans tended to show greater support for federal funding for homelessness and PTSD research when the reference population was military veterans. That study, however, suggests that the effect of the veteran status cue is sensitive to the topic in question.

@@

```{r}
#| label: tbl-demog
#| tbl-cap: "Sample Demographics"
#| tbl-colwidths: [70]

df <- data |>
  dplyr::mutate(
    mil = dplyr::case_when(
      milserv1 =="Yes" & milserv2 == "Yes" ~ "Active Duty",
      milserv1 =="Yes" & milserv2 == "No" ~ "Prior Service (Veteran)",
      milservfam == "Yes" ~ "Has Family in Military",
      milservfam == "No" ~ "No Family in Military",
      TRUE ~ NA),
    ideo_3cat = dplyr::case_when(
      ideo %in% c("Extremely Liberal",
                  "Slightly liberal",
                  "Liberal") ~ "Liberal",
      ideo %in% c("Extremely conservative",
                  "Slightly conservative",
                  "Conservative") ~ "Conservative",
      ideo %in% c("Moderate: middle of the road") ~ "Moderate",
      ideo %in% c("Haven't thought much about this") ~ "Unsure",
      TRUE ~ NA)
    ) |> 
  dplyr::select(
    group,
    age_4cat,
    gender_3cat,
    race,
    hisp,
    educ_4cat,
    mil, 
    partyid_3cat,
    ideo_3cat
    ) |> 
  labelled::set_variable_labels(
    age_4cat = "Age groups, in years",
    gender_3cat = "Gender",
    race = "Race",
    hisp = "Is R of Hispanic, Latino, or Spanish origin",
    educ_4cat = "Education",
    mil = "Military Relation",
    partyid_3cat = "Party ID", 
    ideo_3cat = "Political Ideology")

freqs <- df |> 
  dplyr::mutate(dplyr::across(where(is.character), ~as.factor(.))) |>
  purrr::map(janitor::tabyl, show_na = T) |> 
  purrr::map(janitor::adorn_pct_formatting, affix_sign = F)

freqs <- purrr::list_rbind(freqs) |> 
  dplyr::rename(" " = '.x[[i]]',
                "valid percent" = "valid_percent") |>
  dplyr::as_tibble() |> 
  dplyr::mutate(across(where(is.factor), ~as.character(.)))

tinytable::tt(freqs) |>
  tinytable::format_tt(j = "valid percent", replace = "-") |> 
  tinytable::group_tt(i = list(
    "Experiment Condition" = 1,
    "Age" = 3,
    "Gender" = 7,
    "Race" = 11,
    "Hispanic, Latino, or Spanish Origin" = 17,
    "Education" = 21,
    "Military Relation" = 26,
    "Party ID" = 31,
    "Political Ideology" = 35),
    indent = 2
    ) |>
  tinytable::style_tt(fontsize = 0.80, align = "lccc")

@@

# Appendix C: Test of Random Assignment to Experiment Condition {.appendix}

@@

gm <- list(
  list("raw" = "nobs", "clean" = "N", "fmt" = 0),
  list("raw" = "logLik", "clean" = "Log.Lik.", "fmt" = 3),
  list("raw" = "deviance", "clean" = "Deviance", "fmt" = 2),
  list("raw" = "null.deviance", "clean" = "Deviance Null", "fmt" = 2),
  list("raw" = "df", "clean" = "DF", "fmt" = 0),
  list("raw" = "chisq", "clean" = "Chi2", "fmt" = 3),
  list("raw" = "P(>chisq)", "clean" = "P(>chisq)", "fmt" = 3))

tab.logit <- modelsummary::modelsummary(
  list("log(OR)" = m1),
  output = "tinytable",
  estimate = "{estimate}, [{conf.low}, {conf.high}]",
  statistic = NULL,
  coef_map = cmp,
  gof_function = lrm.gof.stats,
  gof_map = gm,
  gof_omit = "AIC|BIC|F|RMSE"
  ) |> 
  tinytable::strip_tt(line = TRUE)

tab.logit |> 
  tinytable::group_tt(i = list(
    "**Age**" = 1,
    "**Gender**" = 4,
    "**Race**" = 6,
    "**Education**" = 11,
    "**Party ID**" = 14), 
    indent = 2
    ) |> 
  tinytable::style_tt(i = 20, line = "b", line_color = "black", line_width = .05) |> 
  # adjust fontsize of text within table
  tinytable::style_tt(fontsize = 0.7, align = "lc") |>
  # finally, format markdown and blank out any NA fillers
  tinytable::format_tt(markdown = T, replace = " ")

@@

# Appendix D: Polychoric Item and Score Correlations of Trust and Distrust {.appendix}

@@

# Appendix E: Predicted Probabilities of Safety Concerns by Treatment Condition {.appendix}

@@

[^9]: See Appendix D for Inter-item correlation analysis.
